### 2018-12-19 README.Rmd
add Zenodo badge

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis-CI Build Status](https://travis-ci.org/slu-openGIS/areal.svg?branch=master)](https://travis-ci.org/slu-openGIS/areal)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/slu-openGIS/areal?branch=master&svg=true)](https://ci.appveyor.com/project/chris-prener/areal)
[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)

>>>>

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis-CI Build Status](https://travis-ci.org/slu-openGIS/areal.svg?branch=master)](https://travis-ci.org/slu-openGIS/areal)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/slu-openGIS/areal?branch=master&svg=true)](https://ci.appveyor.com/project/chris-prener/areal)
[![Coverage status](https://codecov.io/gh/slu-openGIS/areal/branch/master/graph/badge.svg)](https://codecov.io/github/slu-openGIS/areal?branch=master)
[![DOI](https://zenodo.org/badge/152279647.svg)](https://zenodo.org/badge/latestdoi/152279647)
[![CRAN_status_badge](http://www.r-pkg.org/badges/version/areal)](https://cran.r-project.org/package=areal)
